First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-27 ms.tex
New acknowledgement section per DLKs email

\section{Acknowledgements}
This work was supported by NSF grants AST-1410484 and AST-1206552.
DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship
under award AST-1401708.
This scientific work makes use of the Murchison Radio-astronomy 
Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the 
traditional owners of the Observatory site. Support for the MWA comes from the U.S. 
National Science Foundation (grants AST-0457585, PHY-0835713, CAREER-0847753, and 
AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), 
the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for 
All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant 
CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the 
MIT School of Science, the Raman Research Institute, the Australian National University, 
and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand 
Ministry of Economic Development and an IBM Shared University Research Grant). The 
Australian Federal government provides additional support via the Commonwealth Scientific 
and Industrial Research Organisation (CSIRO), National Collaborative Research 
Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic 
Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We 
acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the 
CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the 
International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin 
University and The University of Western Australia, funded by the Western Australian State 
government.

>>>>

\section{Acknowledgements}
This work was supported by NSF grants AST-1410484 and AST-1206552.
DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship
under award AST-1401708.
This scientific work makes use of the Murchison Radio-astronomy Observatory, operated by 
CSIRO. We acknowledge the Wajarri Yamatji people as the traditional owners of the 
Observatory site. Support for the operation of the MWA is provided by the Australian 
Government (NCRIS), under a contract to Curtin University administered by Astronomy 
Australia Limited. We acknowledge the Pawsey Supercomputing Centre which is supported 
by the Western Australian and Australian Governments.
